Methodology for Assessing the State of the Practice for Domain X

### 2020-04-13 StateOfPractice/Methodology/Methodology.tex
commonality analysis for LB
update Methodology

@@

\ad{Still at brainstorm stage.}
\begin{itemize}
\item percentage of total/open/closed issues with assignees -
Visibility/Transparency
\item lines of new code produced per person-day - Productivity
\item lines/pages of new documents produced per person-day - Productivity
\item number of issues closed per person-day - Productivity
\item percentage of comment lines in the code - maintainability \ad{Not Ao's
qualities}
\end{itemize}

>>>>

Instead of only focus on the current status of the above numbers, we may find
the time history of them to be more valuable. For example, the number of
contributors over time, the number of lines of code over time, the number of
open issues over time, etc.

@@

\ad{Still at brainstorm stage.}
\begin{itemize}
\item percentage of total/open/closed issues with assignees -
Visibility/Transparency
\item lines of new code produced per person-month - Productivity
\item lines/pages of new documents produced per person-month - Productivity
\item number of issues closed per person-month - Productivity
\item percentage of comment lines in the code - maintainability \ad{Not Ao's
qualities}
\end{itemize}

In the above calculations, a month can be determined to be 30 days.
